\chapter{Problem Elaboration}

\section{Previous work}
This thesis and its motivation derived from previous work with hybrid games at NTNU, as mention in chapter \ref{ch:introduction}. In particular, Don\'t Panic was well received, but implementation was time consuming and setup during play proved difficult for players\cite{di2012don}. 

Other work done regarding hybrid games are often centered around tabletops\footnote{With \emph{tabletop} we refer to a table computer, such as Microsoft Surface 1.0 or Samsung SUR40} as the central component of the game. Weathergods\cite{bakker2007weathergods}, KnightMage\cite{magerkurth2004towards} and False Prophets\cite{mandryk2002false} are examples of these. Most of these report a positive feedback from users, inclining that hybrid games indeed can utilize the best from both regular and digital games. An article evaluating tabletop game experience for seniors even claim they enjoy hybrid games and get more immersed than with regular games \cite{al2008designing}.

Two framework has been previously developed for creating tabletop board games: ToyVision\cite{marco2012toyvision} and ReacTIVision\cite{kaltenbrunner2007reactivision}. However, their relevance might be dwindling, as tabletops for private use has near to disappeared. Most of the existing work regarding tabletop games was done in the period 2004-2010. Since then, there has been little development around tabletop games and tabletops in general, at least that target to the private consumer marked. Microsoft PixelSense\footnote{Microsoft PixelSense: Microsofts initative for tabletops.}, and their accompanied hardware, Samsung SUR40 is retired, according to their own websites\footnote{\href{http://www.samsung.com/uk/business/business-products/smart-signage/specialised-display/LH40SFWTGC/EN}{www.samsung.com/uk/business/business-products/smart-signage/specialised-display/LH40SFWTGC/EN} displays Samsung SUR40 as no longer available.}. We speculate that the high cost of aqcuiring tabletop devices\footnote{Samsung SUR40 currently goes for about 5000 USD on eBay market} has played a large role.

Hybrid games without tabletops has also been created. The game \emph{"In Search of the Amulet"}\cite{magerkurth2012hybrid} an 8x8 tiled board  implemented with rfid tags was used together with rfid readers inside digital player pawns. The pawns detected its movement and location on the board, and reported it to a computer. Each player here had each their computer functioning as a private space and allowing them to do actions without the other player knowing. In addition, a "public" screen showed information visible for both players. One of the challenges here was the potential intruising effects of the displays, and it was deliberately made to require as little as possible interaction with the digital components in order to uphold the social aspect. The article does not mention any hybrid game platforms being used.

\subsection{Summary}
Hybrid games of various kinds has been tested, prototyped and developed previously. From those articles we've seen, there has been nothing but  positive feedbacks from users, who have found such games entertaining and immersive.

Platforms for developing hybrid games more easily has been made, but these are centered around tabletop environments, which is not suitable for our task, due to their high aqusition cost.

With the exception of \emph{In Search of the Amulet}\cite{magerkurth2012hybrid}, we've been unable to find previous work of hybrid games with simple digital pawns independant of a tabletop device. We have been completely unable to find hybrid game platforms similar to the one we've planned to develop.

\input{chapters/problem/boardgames_commonalities}

\input{chapters/problem/life_cycle}

\input{chapters/problem/challenges}

\input{chapters/problem/requirements}

\newpage