\chapter{Abstract}
Previous work has sparked interest in hybrid games, games that combine video games and traditional board games by using digital surfaces or tangible, digital tokens. Whilst video games provide a rich, dynamic and interactive environment, board games has the advantage of a social face-to-face interaction. Hybrid board games attempts to combine the best of both, providing the dynamic interactivity of digital games with the social aspect of traditional games.

In this thesis a software platform has been made for creating hybrid board games. The goal was to simplify the challenges with creating and implementing game concepts digitally, in combination with integrating tangible digital devices.

The work has resulted in AnyBoard, a JavaScript based platform that is openly available at \href{https://github.com/tomfa/anyboardjs/}{github.com/tomfa/anyboardjs}. A common communication protocol as well as firmware implementations for two different arduino-based chipsets has been developed and tested on mobile surfaces. With the current state of the AnyBoard platform, developers are able to create games using pawns that detect location, display colors and print cards from a mobile-surface game hub, without knowing anything but common web technology. The platform supports integration with any other JavaScript-based game engine or game development tool available.

AnyBoard can be used as is to create hybrid board games, but also has a great potential to become a richer and more potent tool by further implementation.


\textbf{Keywords: hybrid games, board game, tangible interfaces, internet of things, iot}
\newpage